% \documentstyle[12pt]{article}
% 
% \newcommand{\sfrac}[2]{\mbox{$\frac{#1}{#2}$}}
% 
% \parindent 0in
% \parskip 2ex
% 
% \begin{document}
% 
\subsection{Class {\tt CoarseAverage}}

This class sets data on a level equal to an average of the data
on a finer level of refinement wherever the finer level covers the
coarse level, using the averaging operator in section \ref{sec:ilt}.

\begin{itemize}

\item
\begin{verbatim}
void
define(const DisjointBoxLayout& a_fine_domain,
       const DisjointBoxLayout& a_crse_domain,
       int a_numcomps,
       int a_ref_ratio);
\end{verbatim}
{\bf Arguments:}
  \begin{itemize}
  \item
  \verb|a_fine_domain| (not modified): the fine-level grids (valid region).
  \item
  \verb|a_crse_domain| (not modified): the coarse-level grids (valid region).
  \item
  \verb|a_numcomps| (not modified): the number of components of coarse
  and fine data sets.
  \item
  \verb|a_ref_ratio| (not modified): the refinement ratio $n_{ref}$.
  \end{itemize}

\item 
\begin{verbatim}
void
averageToCoarse(LevelData<FArrayBox>& a_coarse_data,
                const LevelData<FArrayBox>& a_fine_data);
\end{verbatim}
Replaces coarse data with the average of fine data, in the valid fine
domain.
{\bf Arguments:}
  \begin{itemize}
  \item
  \verb|a_coarse_data| (modified): coarse data set, destination of averaging.
  \item
  \verb|a_fine_data| (not modified): fine data set, source of averaging.
  \end{itemize}

\end{itemize}


\subsection{Class {\tt CoarseAverageFace}}
Similar to {\tt CoarseAverage}, but averaging face-centered data
instead of cell-centered data. Data on coarse-level faces is computed
as the average of the overlying fine-level faces. Both arithmetic and
harmonic averaging are supported. 
\begin{itemize}
\item
\begin{verbatim}
void define(const DisjointBoxLayout& a_fineGrids,
            int a_nComp, int a_nRef)
\end{verbatim}

\item
\begin{verbatim}
void averageToCoarse(LevelData<FluxBox>& a_coarse_data,
                     const LevelData<FluxBox>& a_fine_data)
\end{verbatim}
averages fine-level data to coarse level using arithmetic averaging

\item
\begin{verbatim}  
void averageToCoarseHarmonic(LevelData<FluxBox>& a_coarse_data,
                             const LevelData<FluxBox>& a_fine_data)
\end{verbatim}
averages fine-level data to coarse level using harmonic averaging

\end{itemize}
